Spatial phylogenetics of Japanese ferns: Patterns, processes, and implications for conservation

### 2021-09-06 ms/data_readme.Rmd
Update MS
- Fix mentions of Honshu
- Change github URL

Code for analyzing the data is available on github:
https://github.com/joelnitta/japan_ferns_biogeo

@@

@@

A list of native, non-hybrid fern specimens housed at the herbarium of the
Museum of Science and Nature, Japan was converted to a community data matrix at
four grain sizes (grid-cells spanning Japan, each 0.1, 0.2, 0.3, or 0.4 degrees
per side). The original list with latitude and longitude of each specimen is not
included here to protect rare and endangered species. The 0.2 degree grain size
was selected for further analysis based on redundancy (ratio of number of
specimens to number of taxa per cell).

@@

Data files were generated from raw data (not included here) using scripts
available at https://github.com/joelnitta/japan_ferns_biogeo, in particular
https://github.com/joelnitta/japan_ferns_biogeo/blob/main/R/process_raw_data.R.

@@

`r fs::path_file(japan_map_points_file)`: Latitude and longitude of points used
to produce a labeled map of Japan. Some points were originally generated using
script at https://github.com/joelnitta/japan_ferns_biogeo/blob/main/R/geocode.R

@@

`r fs::path_file(protected_areas_file)`: Spatial of protected areas in Japan
in GeoPackage format. Original spatial data downloaded from the Japan Ministry
of the Environment
(https://www.biodic.go.jp/biodiversity/activity/policy/map/map17/index.html) and
Ministry of Land, Infrastructure, Transport and Tourism
(https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-A45.html). Categorization of
protected areas generally followed @Kusumoto2017: either "high" (no human
activities allowed at all) or "medium" status (some economic activities allowed
by permit); other areas not meeting these criteria or not including plants were
not considered. Any overlapping areas within the same protection level were
combined, and any areas overlapping between "medium" and "high" were considered
only "high". Code used to categorize areas available at
https://github.com/joelnitta/japan_ferns_biogeo/blob/main/R/process_raw_data.R

@@

## References

>>>>

Code for analyzing the data is available on github:
https://github.com/joelnitta/japan_ferns_spatial_phy

@@

Additional data used in analysis not included in current data package: Data 
including DNA sequences, taxonomy, and breeding system data for native Japanese 
ferns included in the Dryad data package of @Ebihara2019b (https://datadryad.org/stash/dataset/doi:10.5061/dryad.4362p32)
were used in the analysis.

@@

A list of native, non-hybrid fern specimens housed at the herbarium of the
Museum of Science and Nature, Japan was converted to a community data matrix at
four grain sizes (grid-cells spanning Japan, each 0.1, 0.2, 0.3, or 0.4 degrees
per side). The 0.2 degree grain size was selected for further analysis based on 
redundancy (ratio of number of specimens to number of taxa per cell).

@@

Data files were generated from raw data (not included here) using scripts
available at https://github.com/joelnitta/japan_ferns_spatial_phy, in particular
https://github.com/joelnitta/japan_ferns_spatial_phy/blob/main/R/process_raw_data.R.

@@

`r fs::path_file(japan_map_points_file)`: Latitude and longitude of points used
to produce a labeled map of Japan. Some points were originally generated using
script at https://github.com/joelnitta/japan_ferns_spatial_phy/blob/main/R/geocode.R

@@

`r fs::path_file(protected_areas_file)`: Spatial of protected areas in Japan
in GeoPackage format. Original spatial data downloaded from the Japan Ministry
of the Environment
(https://www.biodic.go.jp/biodiversity/activity/policy/map/map17/index.html) and
Ministry of Land, Infrastructure, Transport and Tourism
(https://nlftp.mlit.go.jp/ksj/gml/datalist/KsjTmplt-A45.html). Categorization of
protected areas generally followed @Kusumoto2017: either "high" (no human
activities allowed at all) or "medium" status (some economic activities allowed
by permit); other areas not meeting these criteria or not including plants were
not considered. Any overlapping areas within the same protection level were
combined, and any areas overlapping between "medium" and "high" were considered
only "high". Code used to categorize areas available at
https://github.com/joelnitta/japan_ferns_spatial_phy/blob/main/R/process_raw_data.R

@@

References
